%% TODO: Write this

%% Conclusions from ACSA
\begin{comment}
\section{Conclusions}

The Anticommutator Spin Algebra, which is a special Jordan
algebra, has many implications. The first of these is the fact
that this algebra is a consistent fermionic algebra which is not a
superalgebra.
% The
%bosonic and fermionic generators $B, F$ in a superalgebra obey:
%\bea
%[B,B] & = & B \nonumber \\ \nonumber
%[F,B] & = & F \\ \nonumber
%\{F,F\} & = & B \nonumber
%\eea
%whereas in ACSA this relation is of the form:
%\[
%\{F,F\} = F
%\]
%which shows how different it is from a superalgebra.
For possible physical applications the right-hand side of the
defining relations (\ref{eqn:defrel1}-\ref{eqn:defrel3}) must also
be supplied with an $\hbar$. In a superalgebra approach where the
$J_i$ are regarded as odd operators, the $\hbar$ on the right-hand
side should also be regarded as an operator anticommuting with the
$J_i$. These models \cite{leites,batalin} result from the
quantization of the odd Poisson bracket. In our approach however,
the concept of grading and therefore an underlying Poisson bracket
formalism does not exist. In particular, there is no Jacobi
identity. Nevertheless, the associative algebra we consider is
consistent with quantum mechanics where physical observables
correspond to hermitian operators and their eigenvalues to
possible results of physical measurement of these observables. It
is for this reason that ACSA suggests a new kind of statistics
which, we believe, will be useful in physics.

The second implication is the important role of quantum groups in
mathematical physics. As we have shown in this paper, the
invariance group of ACSA turns out to be a quantum group. Given
the fact that ACSA is very similar to normal spin algebra and that
the invariance group of spin algebra plays an important role in
physics, the invariance quantum group of ACSA, $SO_{q=-1}(3)$,
becomes a prime example of how central quantum groups have become
in mathematical physics. It is also interesting to note that more
algebras like ACSA can be constructed where the commutators of the
original Lie algebra are turned into anticommutators and that such
algebras might also have invariance quantum groups that is the
same as the invariance group of the original Lie algebra with
$q=-1$. This possibility is open to investigation in a more
general framework.
\end{comment}

% From BISP and FIO paper
\begin{comment}
\section{Discussion}
As we have shown, the boson and fermion algebras can be obtained
as a limit of the inhomogeneous quantum groups \BISp and \FIO. We
can understand why these boson and fermion algebras are not
quantum groups from this construction, since in this limit the
quantum group becomes singular and the antipode does not exist.
Thus we can consider these quantum groups as deformations with a
Hopf algebra structure of their respective particle algebras. This
construction is similar to $q$-deforming the bosonic oscillator to
obtain Pusz-Woronowicz \cite{puszwor} oscillators and then
constructing the $q$-deformed quantum unitary groups as their left
modules. Similarly, in that construction, the $q$-deformed
oscillator can be reobtained as a limit of these $q$-deformed
quantum unitary groups. However, unlike that construction the
quantum groups presented in this paper are inhomogeneous quantum
groups.

Finally, we would like to remark that the widely used field
theoretical generalization achieved by extending the discrete
indices $i, j, k$ to continuous variables together with a
replacement of the Kr\"onecker deltas to Dirac delta functions is
also applicable to the quantum groups we have presented. In this
respect, these quantum groups are also different from the
Pusz-Woronowicz oscillators which cannot be extended to continuous
indices.

We believe that the establishment of these and similar quantum
groups in field theory will be helpful in generalizing methods of
quantization. These approaches will yield a more consistent
approach to interacting field theory and will be the subject of
further investigations.

\end{comment}

The importance of Lie groups in physics arises from the fact that
they are invariance groups of classical physical systems. Thus, for
example, the 3 dimensional position space, the 3 dimensional momentum
space and the 3 dimensional angular momentum space are all transformed
under the same Lie group $SO(3)$. When the classical system is
quantized one realizes that although the resulting quantum system
is invariant under the classical group $SO(3)$, one should also 
perhaps generalize the definition of a Lie group such that the
transformation matrix may have non-commuting entities. This is 
precisely what has been considered in this work. If one considers
the angular momentum algebra and tries to find such a non-commutative
quantum group which leaves the commutation relations of the Lie algebra
invariant, one finds that the elements of the transformation matrix
should be commutative and reobtain the classical group $SO(3)$. On the
other hand, as we have shown, when one considers the anticommuting
spin algebra, its invariance quantum group becomes $SO_{-1}(3)$.
It is also interesting to note that more
algebras like the anticommuting spin algebra can be constructed
where the original Lie algebra is turned into a similar Jordan
algebra. These might also have invariance quantum groups that is the
same as the invariance group of the original Lie algebra in the
limit $q=1$. This possibility is open to investigation in a more
general framework.

As far as the momentum and position are concerned, one realizes that
the Heisenberg algebra inevitably contains the unit operator
and therefore the transformations considered on that algebra should 
be inhomogeneous. It was shown
in this work that this approach indeed makes sense by explicitly
calculating the invariance quantum groups of the bosonic and fermionic
oscillator algebras. In 3 dimensions, the hermitian and antihermitian parts
of the annihilation operator can be identified with the position and 
$i$ times the momentum operator, respectively. For this reason, the
invariance quantum group \BISp that was introduced becomes the invariance
quantum group of the quantum phase space in 3 dimensions. Both
the fermionic and the bosonic inhomogeneous quantum groups considered
in this work are relevant for field theoretical systems; especially since
they can be made infinite dimensional. This is achieved by 
extending the discrete indices $i, j, k$ in \BISp and \FIO 
to continuous  variables together with a replacement of 
the Kr\"onecker deltas to Dirac delta functions. 


As was shown, the boson and fermion algebras can be obtained
as a limit of the inhomogeneous quantum groups \BISp and \FIO. We
can understand why these boson and fermion algebras are not
quantum groups from this construction, since in this limit the
quantum group becomes singular and the antipode does not exist.
Thus we can consider the invariance quantum groups 
as deformations, with a Hopf algebra structure, of their 
respective particle algebras. This
construction is similar to $q$-deforming the bosonic oscillator to
obtain Pusz-Woronowicz \cite{puszwor} oscillators and then
constructing the $q$-deformed quantum unitary groups as their left
modules. Similarly, in that construction, the $q$-deformed
oscillator can be reobtained as a limit of these $q$-deformed
quantum unitary groups. However, in contrast to that construction the
quantum groups presented in this paper are inhomogeneous quantum
groups.

Lastly, we would like to remark on the definition of a quantum group.
Although in most works, quantum groups are defined as noncocommutative
and noncommutative Hopf algebras, this definition does not produce
any physical insight. It makes more sense to define a quantum group as
a Hopf algebra which is a left and/or right module of a physical
algebra obtained by quantizing a classical system. This thesis has directly
dealt with such quantum groups.





