%
% This is a template for the fbe_tez.sty, v4.1 (and maybe later).
%
%
\documentclass[12pt]{report}

% Main Thesis Layout style
\usepackage{fbe_tez}

% The following are needed for chapter3
\usepackage{amscd}
\usepackage{amsmath}
\usepackage{amssymb}

% For multi-line comments
\usepackage{verbatim}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\bean}{\begin{eqnarray*}}
\newcommand{\eean}{\end{eqnarray*}}

\newcommand{\adag}{a^{\dagger}}
\newcommand{\bdag}{b^{\dagger}}
\newcommand{\ket}[1]{\mid #1\;\rangle}
\newcommand{\bra}[1]{\langle\; #1\mid}
\newcommand{\braket}[2]{\langle\; #1\mid #2\;\rangle}
\newcommand{\delfn}[1]{\delta(#1)}
\newcommand{\kro}[1]{\delta_{#1}}
\newcommand{\anti}[2]{\{#1, #2\}}


\def\IC{\mathbb{C}}
\def\IR{\mathbb{R}}
\def\I1{\mathbb{I}}
\def\II{\mathbb{J}}
\def\FIO{$FIO(2d, \IR)\;$}
\def\BISp{$BISp(2d, \IR)\;$}

%
% LaTeX 2.09 users: Replace the above two lines with the following line
%\documentstyle[12pt,fbe_tez]{report}
%
% Declarations
%
%\title{QUANTUM GROUP INVARIANCE OF SOME PHYSICAL ALGEBRAS}
\title{QUANTUM GROUP STRUCTURES ASSOCIATED WITH INVARIANCES OF SOME PHYSICAL ALGEBRAS}
\turkcebaslik{BAZI F\.{I}Z\.{I}KSEL CEB\.{I}RLER\.{I}N 
  DE\~G\.{I}\c{S}MEZL\.{I}\~G\.{I} \.{I}LE \.{I}LG\.{I}L\.{I} KUANTUM GRUP YAPILARI}
\degree{
B.S. in Physics, Bo\~ gazi\c ci University, 1997 \\
B.S. in Mathematics, Bo\~ gazi\c ci University, 1997
}
\author{Ufuk Kayserilio\~ glu}
% The \program declaration is needed only for M.S. theses
%\program{FBE Program for which the Thesis is Submitted}
%\subyear{20xx}
%
% Declare relevant examiners
%
\supervisor{Prof. Dr. Metin Ar\i k}
%\cosuperi{Title and Name of Cosupervisor I}
%\cosuperii{Title and Name of Cosupervisor II}
\examineri{Prof. Dr. \"Omer Faruk Day{\i}}
\examinerii{Prof. Dr. Fahr\"{u}nisa Neyzi}
\examineriii{Prof. Dr. Cihan Sa\c{c}l{\i}o\~{g}lu}
\examineriv{Do\c{c}. Dr. Teoman Turgut}
%\examinerv{Title and Name of Examiner}
\dateofapproval{Day.Month.Year}

\begin{document}
\pagenumbering{roman}
%
% Choose the relevant one
%\makemstitle        % For M.S. theses
\makephdtitle      % For Ph.D. theses
%\makeproposaltitle % For Proposals

\makeapprovalpage

\begin{acknowledgements}
\begin{comment}
For my loving wife Emi for all her support; my wise and understanding mentor Metin Bey for
teaching me a lot of what I know.
\end{comment}
\end{acknowledgements}

\begin{abstract}
Type your abstract here.
\end{abstract}
%
% The usage of the "foreword" and "preface" environments are similar
% the "abstract" and "acknowledgements". See FBE manual for the
% correct order of these pages in the thesis.
%
\begin{ozet}
T\"urk\c ce tez \"ozetini buraya yaz\i n\i z.
\end{ozet}

\tableofcontents
\listoffigures
\listoftables

\begin{symabbreviations}
% The title will be typeset as "LIST OF SYMBOLS/ABBREVIATIONS".
% If you prefer it as "LIST OF SYMBOLS" or "LIST OF ABBREVIATIONS"
% use the environments "symbols" or "abbreviations", respectively.
%
% Use a separate \sym command for each symbols definition.
% First Latin symbols in alphabetical order
\sym{$a_{ij}$}{Description of $a_{ij}$}
% Then Greek symbols in alphabetical order
\sym{$\alpha$}{Description of $\alpha$}
\sym{}{}       % Separating line between symbols and abbreviations
\sym{DA}{Description of abbreviation}
\end{symabbreviations}

\chapter{INTRODUCTION}
\pagenumbering{arabic}

\input{chapter1}

\chapter{THE ANTICOMMUTING SPIN ALGEBRA}

\input{chapter2}

\chapter{QUANTUM GROUPS ASSOCIATED WITH INVARIANCE OF NON-DEFORMED OSCILLATORS}

\input{chapter3}

\chapter{CONCLUSIONS}

\input{chapter4}

\appendix      % Starts appendices
\chapter{A FERMION LIKE ALGEBRA}

\input{appendix1}

\begin{thebibliography}{9}

%% References for Chapter 2

\bibitem{sklyanin}
E.K. Sklyanin, \textit{Funct. Anal. Appl.}, {\bf 16} (1982) 263

\bibitem{frt}
L.D. Fadeev, N.Y. Reshetikhin, L.A. Takhtajan,
\textit{Quantization of Lie Groups and Lie Algebras}, preprint
LOMI, {\bf E-14-87} (1987)

\bibitem{drinfeld}
V.G. Drinfeld, \textit{Quantum Groups}, Proc. Int. Congr. Math.,
Berkeley 1, 798 (1986)

\bibitem{woronowicz}
S.L. Woronowicz, \textit{Commun. Math. Phys.}, {\bf 111} (1987)
613

\bibitem{manin}
Yu I. Manin, \textit{Quantum Groups and Non-commutative Geometry}
(CRM, Montreal University Press, 1988)

\bibitem{jx}
S. Jing, J. Xu, \textit{J. Phys. A: Math. Gen.}, {\bf 24} (1991)
L891

\bibitem{xh}
W.Y. Chan, C.L. Ho, \textit{J. Phys. A: Math. Gen.}, {\bf 26}
(1993) 4827

\bibitem{sm}
A. Solomon, R. McDermott, \textit{J. Phys. A: Math. Gen.}, {\bf
27} (1994) 2619

\bibitem{chung}
W.S. Chung, \textit{Phys. Lett. A}, {\bf 259} (1999) 437

\bibitem{nt}
T Nassar and O Tirkkonen, \textit{J. Phys. A: Math. Gen.}, {\bf31}
(1998) 9983

\bibitem{gppr}
H Grosse, S Pallua, P Prester and E Raschhofer, \textit{J. Phys.
A: Math. Gen.}, {\bf27} (1994) 4761

\bibitem{bnnpsw} J. Balog, M. Niedermaier, F. Niedermayer, A. Patrascioiu, E. Seiler and P. Weisz,
\textit{Nuclear Physics B}, {\bf618} (2001) 315

\bibitem{ubriaco}
M. R. Ubriaco, \textit{Phys. Rev. E}, {\bf58} (1998) 4191

\bibitem{leites}
D. A. Leites, I. M. Shchepochkina, \textit{Theor. Math. Phys.},
{\bf 3}, (2001) 281

\bibitem{batalin}
I. Batalin, I. Tyutin, “Generalized field–antifield formalism,”,
Topics in Statistical and Theoretical Physics (R. Dobrushin et
al., eds.) (Trans. Am. Math. Soc., Ser. 2, Vol. 177), Am. Math.
Soc., Providence, RI (1996), 23

%% References for Chapter 3

\bibitem{fadeev}
V. G. Drinfeld, \textit{Proc. Int. Congr. Math.}, Berkeley {\bf
1}, 798 (1986)

M. Jimbo, \textit{Lett. Math. Phys.} {\bf 11}, 247 (1986)

S. L. Woronowicz, \textit{Commun. Math. Phys.} {\bf 111}, 613
(1987)

L.D. Fadeev, N.Y. Reshetikhin, L.A. Takhtajan, "Quantization of
Lie Groups and Lie Algebras", \textit{Leningrad Math. J.} {\bf 1},
193 (1987)

\bibitem{sww}
M. Schlieker, W. Weich and R. Weixler, \textit{Z. Phys. C} {\bf
53}, 79 (1992)

\bibitem{pw}
P. Podles and S. L. Woronowicz, \textit{Commun. Math. Phys.} {\bf
185}, 325 (1997)

\bibitem{unruh}
W. G. Unruh, \textit{Phys. Rev. D} {\bf14}, 870 (1976)

\bibitem{hawking}
S. W. Hawking, \textit{Phys. Rev. D} {\bf 14}, 2460 (1976)

\bibitem{agy}
M. Arik, S. Gun, A. Yildiz, \textit{Eur. Phys. J. C} {\bf 27}, 453
(2003)

\bibitem{ab}
M. Arik, A. Baykal, \textit{J. Math. Phys.} {\bf 45}, 4207 (2004)

\bibitem{inonu}
E.Inonu and E.P.Wigner, \textit{Proc. Natl. Acad. Sci. U.S.A.}
{\bf 39}, 510 (1953)

\bibitem{majid}
S. Majid, "Braided groups and algebraic quantum field theories",
\textit{Letters in Math. Phys.} {\bf 22}, 167 (1991)

\bibitem{puszwor}
W. Pusz and S.L. Woronowicz, \textit{Rep. Math. Phys.} {\bf 27},
231 (1989)

M. Arik, \textit{Z. Phys. C} {\bf 51}, 627 (1991)

%% References for Chapter 4



\end{thebibliography}
%
% You can also try harvardbibliography, bibnotcited and
% harvardbibnotcited environments for other types of bibliographical
% lists.
%
\end{document}
